\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/train.tex
pass over sec 6 complete.

\begin{table}
\begin{tabular}{c|c|c|c |c|c| c}
  Stage         &  LAN (s) & WAN (s) & Comm. (Mb)  & depth & \#Gates & LOC\\
\hline
1    &  175       & 662        & 29816       & 16370    & 33m    & 500  \\
\hline
2    &  193        & 1095        & 31945        & 30916    & 37m & 516 \\
\hline
3    &  178        & 627        & 29810        & 16369    & 32m  & 478  \\
\hline
Total    &  546      & 2384        & 91571        & --    & 102m & 1494 \\
\end{tabular}

@@

We observe that in the LAN setting, we are about 19 times faster than~\cite{valeriaMatrix} and in the WAN
setting we are about 4 times faster. The main source of these significant speedups is that, unlike~\cite{valeriaMatrix}, \tool does not need to convert the functionality into boolean circuits. 
However, this benchmark requires more lines of code than the previous benchmarks.
It is inconvinient to write Batcher's sort in an iterative language (about 450 lines of \tool).
The size of a recursive implementation would be much slower.
In the future, we would like to add support for functions and recursion.
However, the current programmer effort seems miniscule compared to the mammoth implementation effort
put in by Nikolaenko et al. (Section 5 of ~\cite{valeriaMatrix}) to scale a boolean circuit based
crypto-backend to this benchmark.

>>>>

\begin{table}
\begin{tabular}{c|c|c|c |c|c| c}
  Stage         &  LAN (s) & WAN (s) & \thead{Comm. \\ (Mb)}  & depth & \#Gates & LOC\\
\hline
1    &  175       & 662        & 29816       & 16370    & 33m    & 500  \\
\hline
2    &  193        & 1095        & 31945        & 30916    & 37m & 516 \\
\hline
3    &  178        & 627        & 29810        & 16369    & 32m  & 478  \\
\hline
Total    &  546      & 2384        & 91571        & --    & 102m & 1494 \\
\end{tabular}

@@

We observe that in the LAN setting, we are about 19 times faster than~\cite{valeriaMatrix} and in the WAN
setting we are about 4 times faster. The main source of these significant speedups is that, unlike~\cite{valeriaMatrix}, \tool does not need to convert the functionality into boolean circuits. 
However, this benchmark requires more lines of code than the previous benchmarks.
It is inconvinient to write Batcher's sort in an iterative language (about 450 lines of \tool).
The size of a recursive implementation would be much slower.
In the future, we would like to add support for functions and recursion. \nc{Should we say this in the implementation section or something and not bring it up in the experiments section? Also, do reviewers sometimes say ``Why didnt you do that also?'' Anyway to prevent that?}
However, the current programmer effort seems miniscule compared to the mammoth implementation effort
put in by Nikolaenko et al. (Section 5 of ~\cite{valeriaMatrix}) to scale a boolean circuit based
crypto-backend to this benchmark.
